---
title: "Workflows"
author: "Beth Davis"
repository: "livingcode"
date_created: "2/3/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Google Drive to R Workflow
This workflow developed by Camila Vargas at http://github.com/padl-project and allowed use with permission

First, prepare packages. These lines check if a package is already installed on your computer and if not, installs and loads them.

```{r}
if (!require("googledrive")) {install.packages("googledrive"); require("googledrive")}
if (!require("here")) {install.packages("here"); require("here")}
if (!require("data.table")) {install.packages("data.table"); require("data.table")}
if (!require("tidyverse")) {install.packages("tidyverse"); require("tidyverse")}
if (!require("readxl")) {install.packages("readxl"); require("readxl")}
if (!require("janitor")) {install.packages("janitor"); require("janitor")}
if (!require("lubridate")) {install.packages("lubridate"); require("lubridate")}
```

Using functions from the googledrive package, select your folder and check contents
If you have not yet used the googledrive package, it will ask you to log-in to your googledrive account. Once you have logged in, you can simply select which account you want to use

```{r}
# Copy paste the url of the folder where the data lives
folder_url <- "https://drive.google.com/drive/folders/1I9k7bFI9VBudAyYFxAv1WGs4ELgEJ6ZS"
# list of files inside the folder
files <- drive_ls(as_id(folder_url))
```

This checks whether or not a directory exists in your current path. If the specified directory name is not found, the "if" statement will create it. The rest of the workflow will use the specified directory as the destination for our files

```{r}
if (!dir.exists(here::here("/data"))){
  dir.create(paste0(getwd(),"/data"))
}

## If necessary create a sub directory inside the raw_data. Helpful for separating packages or sub-projects within an overall project

dir.create(paste0(getwd(),"/data/skillshare"))

setwd("~/../Desktop/GitHub/livingcode/data/skillshare")
```


If there are unrecognized Google MIME types, it may not download properly
```{r}
## Download each file to local computer
purrr::walk2(
    map(files$id, as_id),
    paste0(files$name),
    drive_download,
    overwrite = TRUE)
```

```{r}
## Download each file to local computer - this will also rename the file to add the folder name to the beginning of the file name
purrr::walk2(
    map(files$id, as_id),
    paste0("skillsharedata_", files$name),
    drive_download,
    overwrite = TRUE)
```



